Cap On Student Visas in Canada Show Significant GDP Loss

### 2024-04-09 paper/paper.qmd
Final Changes to the Paper

The inflation data was filtered like @tbl-cleaned-data. The original data included all the dates, so it was filtered to only include the year.
```{r}
#| label: tbl-cleaned-data
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: "Sample of Inflation Rate Data"
library(kableExtra)

@@

The consumption cleaned dataset looked like this @tbl-cleaned-data2. The data transposed to have years and consumption have vertical columns instead of horizontal. Only the Year and consumption column of the original dataset were kept and the rest were deleted. Some of the unnecessary first and last rows were also removed from the dataset.

@@

options(kableExtra.latex.max.width=1)
head(consumption, 6) |>
  kable(
        col.names = c("", "Year","Consumption"),
    booktabs = TRUE,
    longtable = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down"), font_size = 6)
```
Some of the other datasets like exports and imports, house_price_index and revenue were also cleaned like the consumption dataset.

@@

## Predictions
Using the model we created and trained, we predicted the GDP of Canada for 2024 given the economical constraints of 2024 as seen in @fig-prediction. The predicted GDP for the given data is: `r predicted_gdp`
```{r}
#| echo: false
#| eval: true
#| label: fig-prediction
#| fig-cap: "Predicted GDP for the Next Year along with Previous Years' Values"
#| warning: false
#| 
new_data1 <- data.frame(
  Total_Unique_Persons = 360000, # Cap on Total_Unique_Persons
  Annual_Change_GDP = 1.5000,
  Revenue = 13971.575,
  House_Price_Index = 124.4,
  Consumption = 63372.4,
  Exports = 779216,
  Unemployment_rate = 5.400,
  Inflation_Rate = 3.6200 # Adjusted variable name without line continuation
)

@@

```
As seen, the GDP decreases quite drastically given the number of fewer students entering the country.

>>>>

The inflation data was filtered like @tbl-cleaned-data. The original data included all the dates, so it was filtered to only include the Year column.
```{r}
#| label: tbl-cleaned-data
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: "Sample of Inflation Rate Data"
library(kableExtra)

@@

The consumption cleaned dataset looked like this @tbl-cleaned-data2. The data transposed to have years and consumption have vertical columns instead of horizontal. Only the Year and Consumption column of the original dataset were kept and the rest were deleted. Some of the unnecessary first and last rows were also removed from the dataset.

@@

options(kableExtra.latex.max.width=1)
head(consumption, 6) |>
  kable(
        col.names = c("", "Year","Consumption"),
    booktabs = TRUE,
    longtable = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down"), font_size = 6)
```
Some of the other datasets like Exports and Imports, House_Price_Index and Revenue were also cleaned like the consumption dataset.

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-prediction
#| fig-cap: "Predicted GDP for the Next Year along with Previous Years' Values"
#| warning: false
#| 
new_data1 <- data.frame(
  Total_Unique_Persons = 360000, # Cap on Total_Unique_Persons
  Annual_Change_GDP = 1.5000,
  Revenue = 13971.575,
  House_Price_Index = 124.4,
  Consumption = 63372.4,
  Exports = 779216,
  Unemployment_rate = 5.400,
  Inflation_Rate = 3.6200 # Adjusted variable name without line continuation
)

@@

## Predictions
Using the model we created and trained, we predicted the GDP of Canada for 2024 given the economical constraints of 2024 as seen in @fig-prediction. The predicted GDP for the given data is: `r predicted_gdp`million (CAD).
As seen, the GDP decreases quite drastically given the number of fewer students entering the country.
